---
title: "What the package does"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{What the package does}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH.4753.113499560)
```

# Introduction
This package was developed as part of the curriculum for MATH 4753 at the University of Oklahoma. It contains many functions which reflect the r tools and statistical methods that I learned over the course of the semester. It also contains a data set that was included as a proof of concept that it can be packaged

# Data
The data set included with this package is called fire.R which contains data about distance from fire stations and damage caused by fires
```{r}
fire
```

# Function Examples
## mybin
This function performs the given number of iterations of the specified binomial experiment and outputs a histogram of the results
```{r}
mybin(100,20,0.7)
```

## myboot2
This function makes bootstrap intervals of the given number of iterations using the given data, function, and alpha value and displays the interval on a histogram
```{r}
myboot2(iter=10000,x=fire$DISTANCE,fun="var",alpha=0.2)
```

## mycltb
This function plots the histogram of the number successes in each iteration of the specified binomial experiment and then plots a normal curve over the histogram for comparison
```{r}
mycltb(n=5,iter=10000,p=0.3)
```

## mymaxlik
This function graphically finds the maximum likelihood estimate for a given function, data, and check intervals
```{r}
y=c(3,3,4,3,4,5,5,4)
logbin=function(x,param) log(dbinom(x,prob=param,size=20))
mymaxlik(x=y,lfun="logbin",param=seq(0,1,length=1000))
```

## myncurve
This function graphically displays the lower-tail probability of the last argument given the mean and standard deviation of a normal distribution
```{r}
myncurve(5,2,4)
```

## scatterhist
This function plots a scatter plot of the given x and y variables and displays the histograms associated with both the x and y variables next to the scatter plot
```{r}
with(fire, scatterhist(DISTANCE,DAMAGE, xlab="DISTANCE"))
```
